\beginsong{Frosty the Snow Man}

\ifchorded
	\gtab{G}{320003:210003}
	\gtab{D7}{XX0212:000213}
	\gtab{C}{X32010:032010}
	\gtab{D}{XX0232:000132}
	\gtab{Bm}{2:X(13321):00342}
	\gtab{Am}{X02210:002310}
	\gtab{D&dim}{X42020:041020}
	\gtab{Em}{022000:012000}
\fi

\beginverse
\[G]Frosty the Snow Man, was a \[C]jolly happy \[G]soul
With a \[C]corn-cob pipe and a \[G]button nose
and two \[C]eyes made \[D7]out of \[G]coal.
\endverse

\beginverse
^Frosty the Snow Man, is a ^fairy tale they ^say
He was ^made of snow but the ^children know
how he ^came to ^life one ^day.
\endverse

\beginverse*
[Bridge]
There \[C]must have been some \[Bm]magic in that \[Am]old silk hat they \[G]found,
For \[D]when they put it \[D&dim]on his head he \[Em]began to dance \[D]around.
\endverse

\beginverse
Oh, ^Frosty the Snow Man was ^alive as he could ^be,
And the ^children say he could ^laugh and play
just the ^same as ^you and ^me.
\endverse

\beginverse*
[Alt]
\[G]Thumpety \[mute]{thump thump}, \[G]thumpety \[mute]{thump thump}, 
\[G]Look at Frosty \[D7]go.
\[D7]Thumpety \[mute]{thump thump}, \[D7]thumpety \[mute]{thump thump}, 
\[D7]over the hills of \[G]snow.
\endverse

\beginverse
^Frosty the Snow Man, knew the ^sun was hot that ^day,
So he ^said, "let's run and we'll ^have some fun
now be^fore I ^melt ^away."
\endverse

\beginverse
^Down to the village, with a ^broomstick in his ^hand,
Running ^here and there all ^around the square,
saying ^"Catch me if ^you ^can."
\endverse

\beginverse*
[Bridge]
He \[C]led them down the \[Bm]streets of town right \[Am]to the traffic \[G]cop
And he \[D]only paused a \[D&dim]moment when he \[Em]heard him holler, \[D]"stop!"
\endverse

\beginverse
^Frosty the Snow Man had to ^hurry on his ^way,
but he ^waved good-bye, saying, ^"Don't you cry;
I'll be ^back ^again some ^day."
\endverse

\beginverse*
[Alt]
\[G]Thumpety \[mute]{thump thump}, \[G]thumpety \[mute]{thump thump}, 
\[G]Look at Frosty \[D7]go.
\[D7]Thumpety \[mute]{thump thump}, \[D7]thumpety \[mute]{thump thump}, 
( PAUSE )
\[D7]over the hills of \[G]snow.
\endverse

\endsong
