\beginsong{Here we come a wassailing}[]
\ifchorded
	\gtab{D}{XX0232:000132}
	\gtab{A7}{X02020:001020}
	\gtab{G}{320003:210003}
	\gtab{Em}{022000:012000}
	\gtab{A}{X02220:001230}
	\gtab{B7}{X21202:021304}
\fi

\musicnote{tempo 1/4=110bpm Jaunty}

\beginverse
\[D]Here we come a wassailing,
among the \[A7]leaves so \[D]green.
\[G]Here we \[D]come a \[A7]wandering,
so \[Em]fair to be \[A]seen.
\endverse

\beginchorus
\[A7]Love and \[D]joy \[G]come to \[D]you,
\[A]and to \[D]you your \[G]wassail \[D]too;
\[A7]And God \[D]bless \[B7]you, and \[Em]send \[S7]you, a \[D]happy New \[A]Year.
\[A7]And God \[D]send \[B7]you a \[Em]happy \[A]New \[D]Year.
\endchorus

\beginverse
^Our wassail cup is made
of the ^rosemary ^tree;
^And so ^is your ^beer,
of the ^best bar^ley.
\endverse

\beginverse
^We are not daily beggars,
that beg from ^door to ^door.
^But we are ^neightbors' ^children,
chom ^you have seen ^before.
\endverse

\beginverse
^Good master and good mistress
as you ^sit by the ^fire.
^Pray this of us ^poor ^children,
are ^wandering in the ^mire.
\endverse

\beginverse
^We have little purse,
made of ^ratching leather ^skin.
^We want some of your ^small ^change,
to ^line it well with^in.
\endverse

\beginverse
^Call up the Butler of this house,
put ^on his golden ^ring.
^Let him bring us a ^glass of ^beer,
and the ^better we shall ^sing.
\endverse

\beginverse
^Bring us out a table,
and ^spread it with a ^cloth.
^Bring us out a ^moldy ^cheese,
and ^some of your Christmas ^loaf.
\endverse

\beginverse
^God bless the Master of this house,
like^wise the Misteress ^too.
^And alll the ^little ^children,
that ^round the table ^go.
\endverse

\endsong