\beginsong{Jingle Bell Rock}[]

\ifchorded
	\gtab{D}{XX0232:000132}
	\gtab{Dmaj7}{XX0(222):000111}
	\gtab{D6}{XX0202:000102}
	\gtab{Em}{022000:012000}
	\gtab{A7}{X02020:001020}
	\gtab{A}{X02220:001230}
	\gtab{G}{320003:210003}
	\gtab{Gm}{3:(133111):134111}
	\gtab{D7}{XX0212:000213}
	\gtab{E}{022100:012300}
	\gtab{E7}{020100:010200}
	\gtab{B7}{X21202:021304}	
\fi

\beginverse*\newchords{jingleverse}\memorize[jingleverse]
\[D]Jingle bell, \[Dmaj7]jingle bell, \[D6]jingle bell \[D]rock,
\[D6]jingle bell \[D]swing and \[Em]jingle bells \[A7]ring.
\[Em]Snowing and \[A7]blowing up \[Em]bushels of \[A7]fun,
\[A]now the jingle hop \[Em]has be\[A7]gun.
\endverse

\beginverse*\replay[jingleverse]
^Jingle bell, ^jingle bell, ^jingle bell ^rock,
^jingle bells ^chime in ^jingle bell ^time.
^Dancing and ^prancing in ^Jingle Bell ^Square,
^ in the ^frosty ^air.
\endverse

\newchords{jinglechorus}
\beginchorus\memorize[jinglechorus]
what a \[G]bright time, it's the \[Gm]right time,
to \[D]rock the night a-\[D7]way.
Jingle \[E]bell time is a \[E7]swell time,
to \[A]go \[A7]gliding in a \[A]one-horse \[A7]sliegh.
\endchorus

\newchords{jingleverseB}
\beginverse*\memorize[jingleverseB]
\[D]Giddy-up \[Dmaj7]Jingle horse, \[D6]pick up your \[D]feet,
jingle around the \[B7]clock.
\[G]Mix and \[Gm]mingle in the \[E7]jingling \[Gm]beat,
\[Em]that's the \[A]jingle \[A7]bell \[D]rock.
\endverse

\beginverse*\replay[jingleverse]
^Jingle bell, ^jingle bell, ^jingle bell ^rock,
^jingle bells ^chime in ^jingle bell ^time.
^Dancing and ^prancing in ^Jingle Bell ^Square,
^ in the ^frosty \[D]air.
\endverse

\beginchorus\replay[jinglechorus]
What a ^bright time, it's the ^right time,
to ^rock the night a-^way
Jingle ^bell time is a ^swell time,
to ^go ^gliding in a ^one-horse ^sleigh.
\endchorus

\beginverse*\replay[jingleverseB]
{\nolyrics Outro: }
^giddy-up ^jingle horse, ^pick up your ^feet,
jingle around the ^clock.
^Mix and ^mindle in the ^jingling ^beat,
\[Em]that's the \[A]jingle bell,
\[Em]that's the \[A]jingle bell,
\[Em]that's the \[A]jingle \[A7]bell \[D]rock 
{\nolyrics \[D6] \[D]}
\endverse

\endsong